Elliptic operator stability and small cells on finite volume grids

### 2023-04-26 example/DomainDecomposition/EBCellMerge/hoeb_petsc_test/_doc/paper.tex
this is the version I am submitting

\newcommand{\Abold}{{\bf A}}
\newcommand{\abold}{{\bf a}}
\newcommand{\bbold}{{\bf b}}
\newcommand{\cbold}{{\bf c}}
\newcommand{\dbold}{{\bf d}}
\newcommand{\ebold}{{\bf e}}
\newcommand{\fbold}{{\bf f}}
\newcommand{\Fbold}{{\bf F}}
\newcommand{\gbold}{{\bf g}}
\newcommand{\hbold}{{\bf h}}
\newcommand{\ibold}{{\bf i}}
\newcommand{\jbold}{{\bf j}}
\newcommand{\kbold}{{\bf k}}
\newcommand{\lbold}{{\bf l}}
\newcommand{\mbold}{{\bf m}}
\newcommand{\Mbold}{{\bf M}}
\newcommand{\nbold}{{\bf n}}
\newcommand{\obold}{{\bf o}}
\newcommand{\pbold}{{\bf p}}
\newcommand{\qbold}{{\bf q}}
\newcommand{\rbold}{{\bf r}}
\newcommand{\sbold}{{\bf s}}
\newcommand{\tbold}{{\bf t}}
\newcommand{\ubold}{{\bf u}}
\newcommand{\vbold}{{\bf v}}
\newcommand{\wbold}{{\bf w}}
\newcommand{\xbold}{{\bf x}}
\newcommand{\ybold}{{\bf y}}
\newcommand{\zbold}{{\bf z}}
\newcommand{\bigzbold}{{\bf Z}}
\newcommand{\xspace}{\hspace{2 mm}}

\newcommand{\ahat}{{\hat a}}
\newcommand{\bhat}{{\hat b}}
\newcommand{\chat}{{\hat c}}
\newcommand{\dhat}{{\hat d}}
\newcommand{\ehat}{{\hat e}}
\newcommand{\fhat}{{\hat f}}
\newcommand{\ghat}{{\hat g}}
\newcommand{\hhat}{{\hat h}}
\newcommand{\ihat}{{\hat i}}
\newcommand{\jhat}{{\hat j}}
\newcommand{\khat}{{\hat k}}
\newcommand{\lhat}{{\hat l}}
\newcommand{\mhat}{{\hat m}}
\newcommand{\nhat}{{\hat n}}
\newcommand{\ohat}{{\hat o}}
\newcommand{\phat}{{\hat p}}
\newcommand{\qhat}{{\hat q}}
\newcommand{\rhat}{{\hat r}}
\newcommand{\shat}{{\hat s}}
\newcommand{\that}{{\hat t}}
\newcommand{\uhat}{{\hat u}}
\newcommand{\vhat}{{\hat v}}
\newcommand{\what}{{\hat w}}
\newcommand{\xhat}{{\hat x}}
\newcommand{\yhat}{{\hat y}}
\newcommand{\zhat}{{\hat z}}

\newcommand{\abar}{{\bar {\bf a}}}
\newcommand{\bbar}{{\bar {\bf b}}}
\newcommand{\cbar}{{\bar {\bf c}}}
\newcommand{\dbar}{{\bar {\bf d}}}
\newcommand{\ebar}{{\bar {\bf e}}}
\newcommand{\fbar}{{\bar {\bf f}}}
\newcommand{\gbar}{{\bar {\bf g}}}
%\newcommand{\hbar}{{\bar {\bf h}}}
\newcommand{\ibar}{{\bar {\bf i}}}
\newcommand{\jbar}{{\bar {\bf j}}}
\newcommand{\kbar}{{\bar {\bf k}}}
\newcommand{\lbar}{{\bar {\bf l}}}
\newcommand{\mbar}{{\bar {\bf m}}}
\newcommand{\nbar}{{\bar {\bf n}}}
\newcommand{\obar}{{\bar {\bf o}}}
\newcommand{\pbar}{{\bar {\bf p}}}
\newcommand{\qbar}{{\bar {\bf q}}}
\newcommand{\rbar}{{\bar {\bf r}}}
\newcommand{\sbar}{{\bar {\bf s}}}
\newcommand{\tbar}{{\bar {\bf t}}}
\newcommand{\ubar}{{\bar {\bf u}}}
\newcommand{\vbar}{{\bar {\bf v}}}
\newcommand{\wbar}{{\bar {\bf w}}}
\newcommand{\xbar}{{\bar {\bf x}}}
\newcommand{\ybar}{{\bar {\bf y}}}
\newcommand{\zbar}{{\bar {\bf z}}}

\newcommand{\dx}{{h}}
\newcommand{\nph}{{n + \frac{1}{2}}}
\newcommand{\iph}{{\ibold + \frac{1}{2}\ebold_d}}
\newcommand{\ipmh}{{\ibold \pm \frac{1}{2}\ebold_d}}
\newcommand{\imh}{{\ibold - \frac{1}{2}\ebold_d}}

\newcommand{\half}{\frac{1}{2}}
%\newcommand{\Fbold}{\mathbf{F}}
%\newcommand{\iphed}{{\ibold+\half\ebold^d}}
\newcommand{\deriv}{\partial}
\newcommand{\area}{\mathcal{A}}
\newcommand{\R}[1]{\mathbb{R}^{#1}}
\newcommand{\cf}{{\scriptscriptstyle F}}
\newcommand{\cn}{{\scriptscriptstyle N}}
\newcommand{\sEB}{{\scriptscriptstyle EB}}
\renewcommand{\vec}[1]{\mathbf{#1}} % Vector (bold)
\newcommand{\tens}[1]{\mathbf{#1}} % Tensor (bold)
\newcommand{\mat}[1]{\mathbf{#1}} % Matrix (bold)
\newcommand{\hatvec}[1]{\hat{\vec{#1}}} % Vector with a hat (bold)
\newcommand{\ddt}[1]{\frac{\partial #1}{\partial t}} % partial d/dt
\newcommand{\DDt}[1]{\frac{\text{d}#1}{\text{d}t}} % "total" d/dt
\newcommand{\ddr}[1]{\frac{\partial #1}{\partial r}} % d/dr
\newcommand{\ddx}[1]{\frac{\partial #1}{\partial x}} % d/dx
\newcommand{\ddy}[1]{\frac{\partial #1}{\partial y}} % d/dy
\newcommand{\ddz}[1]{\frac{\partial #1}{\partial y}} % d/dz
\newcommand{\ddxi}[1]{\frac{\partial #1}{\partial x_i}} % d/dx_i
\newcommand{\diverg}[1]{\nabla\cdot#1} % Divergence operator
\newcommand{\curl}[1]{\nabla \times #1} % Curl operator
\newcommand{\dOmega}{\text{d}\Omega} % Volume differential (Omega style)
\newcommand{\dV}{\text{d}V} % Volume differential
\newcommand{\dA}{\text{d}A} % Area differential
\newcommand{\labelEq}[1]{\label{eq:#1}\hbox{\tt #1 \quad}} % Use this to label an equation.
\newcommand{\refEq}[1]{(\ref{eq:#1})}   % Use this to reference an equation.
\newcommand{\labelSec}[1]{\label{sec:#1}} % Use this to label a section.
\newcommand{\refSec}[1]{\S\ref{sec:#1}} % Use this to reference a section.
\newcommand{\labelChap}[1]{\label{chap:#1}} % Use this to label a chapter.
\newcommand{\refChap}[1]{Chapter \ref{chap:#1}} % Use this to reference a chapter.
\newcommand{\labelApp}[1]{\label{app:#1}} % Use this to label an appendix.
\newcommand{\refApp}[1]{Appendix \ref{app:#1}} % Use this to reference an appendix.
\newcommand{\ib}{{\bf{i}}}    % bold italic i
\newcommand{\jb}{{\bf{j}}}    % bold italic j
\newcommand{\kb}{{\bf{k}}}    % bold italic k
\newcommand{\lb}{{\bf{l}}}    % bold italic l
\newcommand{\mb}{{\bf{m}}}    % bold italic m
\newcommand{\ub}{{\bf{u}}}    % bold italic u
\newcommand{\xb}{{\bf{x}}}    % bold italic x
\newcommand{\vb}{{\bf{v}}}    % (bold italic) VoF index
\newcommand{\fb}{{\bf{f}}}    % (bold italic) face index
\newcommand{\pb}{{\bf{p}}}    % (bold italic) multi-index p
\newcommand{\qb}{{\bf{q}}}    % (bold italic) multi-index q
\newcommand{\ebd}{{\bf{e}^d}}
\newcommand{\normal}[1]{\vec{n}_{#1}} % Outward normal.
\newcommand{\order}[1]{\mathcal{O}(#1)} % Order notation

\newcommand{\ed}{{\bf{e}_d}}
\newcommand{\Zbold}{{\bf{0}}}
\newcommand{\unitV}{\mathds{1}}
\newcommand{\eb}{\text{EB}}
\newcommand{\EB}{\text{EB}}
\newcommand{\vol}{\mathcal{V}}
\newcommand{\face}{\mathcal{F}}
\newcommand{\cali}{\mathcal{I}}
\newcommand{\calc}{\mathcal{C}}
\newcommand{\zerobold}{{\bf{0}}}
\newcommand{\xz}{{\bf{x}_0}}

\newcommand{\Dim}{D}
\newcommand{\dif}{\mathrm{d}}
\newcommand{\dt}{{\Delta t}}
\newcommand{\avg}[1]{\overline{#1}}
\newcommand{\avgI}[1]{\overline{#1}_{\ibold}}
\newcommand{\imhed}{{\ibold+\frac{1}{2}\ebold_d}}
\newcommand{\ipmhj}{{\ibold\pm\frac{1}{2}\ebold_d}}
\newcommand{\iphj}{{\ibold+\frac{1}{2}\ebold_d}}
\newcommand{\imhj}{{\ibold-\frac{1}{2}\ebold_d}}

\newcommand{\ipfed}[1]{\ibold+\frac{#1}{2}\ebold_d}
\newcommand{\imfed}[1]{\ibold-\frac{#1}{2}\ebold_d}
\newcommand{\ipmfed}[1]{\ibold\pm\frac{#1}{2}\ebold_d}
\newcommand{\eq}[1]{(\ref{#1})}

\newcommand{\nref}{n_{\text{ref}}}
\newcommand{\phio}{\phi^{\circ}}

@@

\title{Polynomial expansions of finite volume data in a cut cell context}
\author{N. Overton-Katz \footnotemark[1]
   \and H. Johansen     \footnotemark[1]
   \and D. T. Graves    \footnotemark[1]
   \and D. Devendran    \footnotemark[2]
   \and O. Anteparra    \footnotemark[1]}

@@

  We discuss the mechanics of forming stable local polynomial
  expansions of finite volume data in the context of cut cell grids.
  We show that significant solvability issues can arise from certain weighting
  functions.    A very rudimentary but stable cell merger algorithm is
  presented as we show that these solvability issues are not 
  an artifact of small-cell instabilties.    We show that one can
  manage these solvability issues with careful algorithm choices.

@@

\section{Introduction}

Embedded boundary (EB) grids are formed when one passes a surface
through a Cartesian mesh.    For sufficiently complex geomtries, these methods
are very attactive because grid generation is a solved problem
and not computationally overwhelming even in a moving-boundary context
\cite{MillerTrebotich2012}.

In the current context, we form the cutting surface as the zero
surface of an implicit function  of space
$I(\xbold) = 0, \xbold \in R^D$.
For smooth ($I$),  moments can be generated to any
accuracy \cite{Schwartz2015}.

@@

To gain insight into the connection between solvability, weighting and
order, we evaluate the matrix
\begin{equation}
A \equiv (WM)^T(WM)
\label{eqn::normalEq}
\end{equation}
at every volume in a computational grid and analyze its
eigenvalues.   Given a matrix $A_i$ with the set of eigenvalues
$\{ \lambda_{i}\}$, the inverse of the condition number $\_i$ is given by
\begin{equation*}
  \cali_i = \frac{|\lambda_i|_{min}}{|\lambda_i|_{max}},
\end{equation*}
which goes to zero as the maximum and minimum eigenvalues diverge and
the matrix becomes more poorly conditioned.   These eigenvalues are
obtained through  SVD decompostion \footnotemark[7].

Solving the normal equations (\ref{eqn::normalEq}) for the
coeffients is not ideal because the $\calc_A$, condition number of $A$ is the
square of the $\calc_{WM}$,  condition number of $WM$  \cite{BigCheese}.  
\begin{equation}
  \calc_A = \calc^2_{WM}
\end{equation}  
SVD can be used to solve the system with the condition number of
$\calc_{WM}$.  That, however, requires interweaving the computation of
the stencil with the target application's equations.  Since we are
doing this analysis independent of a specific target stancil, one should
interpret our condition number results as the square of the effective
condition number that algorithm developers will encounter.

First we  measure   an uncut Cartesian mesh to
provide a baseline without the complications involved with cut cells.
Next we cut the mesh with a very smooth implicit function and do the
same measurements.   Finally we take this cut mesh and merge its small
cells to neighbors to eliminate all cells smaller than a Cartesian
volume to isolate the effects of small cells.

@@

\section{Test description}
\label{sec::eb}

We begin with the simplest possible motivating example: a
$D$-dimensional Cartesian geometry wherein all cells are uncut.
Figure \ref{fig::T3W3} shows all values of $\cali$ for $D=2$, $\cali$ with
$P_w = P_T = 3$.  Table \ref{tab::worst_all_reg_inv_conv} shows the
worst condition number in this simple grid for a number of values of
$P_w$ and $P_T$.

@@

If we use grid volumes at this point, the volume fraction
\begin{equation*}
\kappa_\ibold \equiv V_\ibold/h^D 
\end{equation*}
can be arbitrarily small ($ 0 < \kappa <= 1$).

We can also choose to
merge small volumes with larger neighbors without formal loss of
accuracy. The simple merger we use is described in
described in appendix \ref{appendix::merger}.
When merged using this algorithm, $\kappa$ can be larger than $2^D$.

Without using cell merger, the volume map in two dimensions is shown
in figure \ref{fig::unmerged2dmap}.   With cell merger, that same map
becomes the grid shown in figure{fig::unmerged2dmap}.
Tables \ref{tab::worst_unmerged_inv_conv} and
\ref{tab::worst_merged_inv_conv}
show the worst $\cali$ for the unmerged and merged  grids
respectively while varying $P_w$ and $P_T$.

\begin{figure}
\centerline{\epsfig{figure=_fig/all_reg_t3_w3_inv_cond.ps,width=0.4\linewidth } }
\label{fig::T3W3}
\caption
    {   Values of of the inverse of the condition number
      $\cali_A = 1/\calc_A$
      for an uncut Cartesian $32^2$
      grid where $P_w = P_T = 3$.
      Keep in mind that $\calc_A = \calc^2_{WM}$.
    }
\end{figure}

\begin{small}
\begin{table}
\begin{center}
\begin{tabular}{|cccc|ccc|} \hline
$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$ \\
\hline
2 & 1 & 1 & 3 & 2.280975e+00 & 1.471897e-03 & 6.452929e-04 \\ 
2 & 1 & 2 & 3 & 1.184453e+00 & 1.544110e-04 & 1.303648e-04 \\ 
2 & 1 & 3 & 3 & 1.036586e+00 & 2.327227e-05 & 2.245088e-05 \\ 
2 & 1 & 4 & 3 & 1.008340e+00 & 4.569664e-06 & 4.531869e-06 \\ 
2 & 1 & 5 & 3 & 1.002008e+00 & 1.029556e-06 & 1.027493e-06 \\
\hline
2 & 2 & 1 & 3 & 2.280983e+00 & 1.185321e-06 & 5.196535e-07 \\ 
2 & 2 & 2 & 3 & 1.184453e+00 & 8.194451e-08 & 6.918341e-08 \\ 
2 & 2 & 3 & 3 & 1.036586e+00 & 5.067663e-09 & 4.888801e-09 \\ 
2 & 2 & 4 & 3 & 1.008340e+00 & 3.385548e-10 & 3.357547e-10 \\ 
2 & 2 & 5 & 3 & 1.002008e+00 & 2.634337e-11 & 2.629058e-11 \\ 
\hline
2 & 3 & 1 & 3 & 2.280983e+00 & 5.060791e-10 & 2.218689e-10 \\ 
2 & 3 & 2 & 3 & 1.184453e+00 & 4.179917e-11 & 3.528985e-11 \\ 
2 & 3 & 3 & 3 & 1.036586e+00 & 2.762010e-12 & 2.664525e-12 \\ 
2 & 3 & 4 & 3 & 1.008340e+00 & 1.380647e-13 & 1.369228e-13 \\ 
2 & 3 & 5 & 3 & 1.002008e+00 & 6.886907e-15 & 6.873105e-15 \\ 
\hline
2 & 4 & 1 & 3 & 2.744326e+00 & 2.848432e-25 & 1.037935e-25 \\ 
2 & 4 & 2 & 3 & 1.184453e+00 & 1.481174e-27 & 1.250513e-27 \\ 
2 & 4 & 3 & 3 & 1.055930e+00 & 4.257688e-26 & 4.032168e-26 \\ 
2 & 4 & 4 & 3 & 1.008340e+00 & 1.078564e-23 & 1.069643e-23 \\ 
2 & 4 & 5 & 3 & 1.002008e+00 & 5.873348e-25 & 5.861578e-25 \\ 
\hline
3 & 1 & 1 & 3 & 4.207341e+00 & 3.347096e-03 & 7.955372e-04 \\ 
3 & 1 & 2 & 3 & 1.335375e+00 & 2.299835e-04 & 1.722239e-04 \\ 
3 & 1 & 3 & 3 & 1.058688e+00 & 2.726319e-05 & 2.575186e-05 \\ 
3 & 1 & 4 & 3 & 1.012826e+00 & 4.843834e-06 & 4.782494e-06 \\ 
3 & 1 & 5 & 3 & 1.003042e+00 & 1.052599e-06 & 1.049406e-06 \\ 
\hline
3 & 2 & 1 & 3 & 4.207383e+00 & 2.698941e-06 & 6.414775e-07 \\ 
3 & 2 & 2 & 3 & 1.335376e+00 & 1.349331e-07 & 1.010450e-07 \\ 
3 & 2 & 3 & 3 & 1.058688e+00 & 6.504992e-09 & 6.144388e-09 \\ 
3 & 2 & 4 & 3 & 1.012826e+00 & 3.782273e-10 & 3.734376e-10 \\ 
3 & 2 & 5 & 3 & 1.003042e+00 & 2.753365e-11 & 2.745014e-11 \\ 
\hline
3 & 3 & 1 & 3 & 4.207383e+00 & 1.150489e-09 & 2.734453e-10 \\ 
3 & 3 & 2 & 3 & 1.335376e+00 & 6.641096e-11 & 4.973204e-11 \\ 
3 & 3 & 3 & 3 & 1.058688e+00 & 3.224905e-12 & 3.046133e-12 \\ 
3 & 3 & 4 & 3 & 1.012826e+00 & 1.004670e-13 & 9.919476e-14 \\ 
3 & 3 & 5 & 3 & 1.003042e+00 & 3.476637e-15 & 3.466092e-15 \\ 
\hline
3 & 4 & 1 & 3 & 5.166875e+00 & 1.524000e-25 & 2.949559e-26 \\ 
3 & 4 & 2 & 3 & 1.474014e+00 & 1.231139e-27 & 8.352288e-28 \\ 
3 & 4 & 3 & 3 & 1.102368e+00 & 5.433012e-27 & 4.928491e-27 \\ 
3 & 4 & 4 & 3 & 1.012826e+00 & 1.327379e-23 & 1.310570e-23 \\ 
3 & 4 & 5 & 3 & 1.003042e+00 & 6.807789e-25 & 6.787141e-25 \\
\hline
\end{tabular}
\end{center}
\label{tab::worst_all_reg_inv_conv}
\caption
    {
      We show the lowest value of
      $\cali$ for an entire Cartesian grid of size $32^D$.
      We vary Taylor power $P^T$, weighting
      function exponents $P^W$, and dimensionality $D$.   Keep in mind
      that the effective condition number of the problem will be 
      $C_{WM} = (1/\sqrt(\cali))$.
    }
\end{table}
\end{small}

@@

We show first that for a safe (low) choice of
$P_T$, even the worst condition number in a given grid can be quite
reasonable. With more aggressive choices of $P_T$, $\cali$ can be very
small.  The data also
show clearly that there is a connection between solvability, weighting
function, and polynomial order.  Unexpectedly, we show that for a
fixed polynomial order $P_T$, a higher weighting power $P_w$ can make the
solvability problem worse.

>>>>

\input{abbrev.tex}

@@

\title{Elliptic operator stability and small cells on  finite volume grids}
\author{N. Overton-Katz \footnotemark[1]
   \and H. Johansen     \footnotemark[1]
   \and D. T. Graves    \footnotemark[1]
   \and D. Devendran    \footnotemark[2]
   \and O. Anteparra    \footnotemark[1]}

@@

  Numerical stability for elliptic operators is well understood.  To
  be numerically stable, a numerical operator for an elliptic equation
  cannot have non-zero positive real eigenvalues.  We explore a family
  of elliptic operators and attempt to define the boundaries of
  stability for this family of algorithms.

@@

\section{Introduction}
Embedded boundary (EB) grids are formed when one passes an  surface
through a Cartesian mesh.    For sufficiently complex geomtries, these methods
are very attactive because grid generation is a solved problem
\cite{MillerTrebotich2012}.

Devendran, et al. \cite{Devendran2017} 
  real component of an operator eigenvalue
  Using the basic framework of the elliptic operator in Devendran, et al.
  expansions of finite volume data in the context of cut cell grids.
  We show that significant solvability issues can arise from certain weighting
  functions.    A very rudimentary but stable cell merger algorithm is
  presented as we show that these solvability issues are not 
  an artifact of small-cell instabilties.    We show that one can
  manage these solvability issues with careful algorithm choices.

In the current context, we form the cutting surface as the zero
surface of a function  of space $I(\xbold)$, $\xbold \in R^D$.
For smooth ($I$),  moments can be generated to any
accuracy \cite{Schwartz2015}.

@@

To gain insight into the connection between solvability, weighting and
order, we evaluate the matrix
\begin{equation}
A \equiv (WM)^T(WM)
\label{eqn::normalEq}
\end{equation}
at every volume in a computational grid and analyze its
eigenvalues.   Given a matrix $A_i$ with the set of eigenvalues
$\{ \lambda_{i}\}$, the inverse of the condition number $I_i$ is given by
\begin{equation*}
  I_i = \frac{\lambda_i|_{min}}{\lambda_i|_{max}},
\end{equation*}
which goes to zero as the maximum and minimum eigenvalues diverge and
the matrix becomes more poorly conditioned.   These eigenvalues are
obtained through  SVD decompostion \footnotemark[7].

Solving the normal equations (\ref{eqn::normalEq}) for the
coeffients is not ideal because the condition number of $A$ is the
square of the condition number of
$WM$  \cite{BigCheese}.     SVD can be used to solve the system with
the condition number of $WM$.   That, however, requires interweaving
the computation of the stencil with  the target application's
equations.   Since we are doing this 
analysis in the absence of a
specific target stancil, one should interpret our condition number
results as the square of the effective condition number that algorithm
developers will encounter.

First we  measure   an uncut, Cartesian mesh to
provide a baseline without the complications involved with cut cells.
Next we cut the mesh with a very smooth implicit function and do the
same measurements.   Finally we take this cut mesh and merge its small
cells to neighbors to eliminate all cells smaller than a Cartesian
volume to isolate the effects of small cells.

@@

\subsection{All Regular geometry}

We begin with the simplest possible motivating example: a
$D$-dimensional Cartesian geometry wherein all cells are uncut.
Figure \ref{fig::T3W3} shows all values of $I$ for $D=2$, $I$ with
$P_w = P_T = 3$.  Table \ref{tab::worst_all_reg_inv_conv} shows the
worst condition number in this simple grid for a number of values of
$P_w$ and $P_T$.

\begin{figure}
\centerline{\epsfig{figure=_fig/all_reg_t3_w3_inv_cond.ps,width=0.4\linewidth } }
\label{fig::T3W3}
\caption
    {
      $I$ (inverse of the condition number for matrix $A$ for a $32^2$
      uncut grid where $P_w = P_T = 3$.
    }
\end{figure}

\begin{small}
\begin{table}
\begin{center}
\begin{tabular}{|cccc|ccc|} \hline
$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
\hline
2 & 1 & 1 & 3 & 2.280975e+00 & 1.471897e-03 & 6.452929e-04 \\ 
2 & 1 & 2 & 3 & 1.184453e+00 & 1.544110e-04 & 1.303648e-04 \\ 
2 & 1 & 3 & 3 & 1.036586e+00 & 2.327227e-05 & 2.245088e-05 \\ 
2 & 1 & 4 & 3 & 1.008340e+00 & 4.569664e-06 & 4.531869e-06 \\ 
2 & 1 & 5 & 3 & 1.002008e+00 & 1.029556e-06 & 1.027493e-06 \\
\hline
2 & 2 & 1 & 3 & 2.280983e+00 & 1.185321e-06 & 5.196535e-07 \\ 
2 & 2 & 2 & 3 & 1.184453e+00 & 8.194451e-08 & 6.918341e-08 \\ 
2 & 2 & 3 & 3 & 1.036586e+00 & 5.067663e-09 & 4.888801e-09 \\ 
2 & 2 & 4 & 3 & 1.008340e+00 & 3.385548e-10 & 3.357547e-10 \\ 
2 & 2 & 5 & 3 & 1.002008e+00 & 2.634337e-11 & 2.629058e-11 \\ 
\hline
2 & 3 & 1 & 3 & 2.280983e+00 & 5.060791e-10 & 2.218689e-10 \\ 
2 & 3 & 2 & 3 & 1.184453e+00 & 4.179917e-11 & 3.528985e-11 \\ 
2 & 3 & 3 & 3 & 1.036586e+00 & 2.762010e-12 & 2.664525e-12 \\ 
2 & 3 & 4 & 3 & 1.008340e+00 & 1.380647e-13 & 1.369228e-13 \\ 
2 & 3 & 5 & 3 & 1.002008e+00 & 6.886907e-15 & 6.873105e-15 \\ 
\hline
2 & 4 & 1 & 3 & 2.744326e+00 & 2.848432e-25 & 1.037935e-25 \\ 
2 & 4 & 2 & 3 & 1.184453e+00 & 1.481174e-27 & 1.250513e-27 \\ 
2 & 4 & 3 & 3 & 1.055930e+00 & 4.257688e-26 & 4.032168e-26 \\ 
2 & 4 & 4 & 3 & 1.008340e+00 & 1.078564e-23 & 1.069643e-23 \\ 
2 & 4 & 5 & 3 & 1.002008e+00 & 5.873348e-25 & 5.861578e-25 \\ 
\hline
3 & 1 & 1 & 3 & 4.207341e+00 & 3.347096e-03 & 7.955372e-04 \\ 
3 & 1 & 2 & 3 & 1.335375e+00 & 2.299835e-04 & 1.722239e-04 \\ 
3 & 1 & 3 & 3 & 1.058688e+00 & 2.726319e-05 & 2.575186e-05 \\ 
3 & 1 & 4 & 3 & 1.012826e+00 & 4.843834e-06 & 4.782494e-06 \\ 
3 & 1 & 5 & 3 & 1.003042e+00 & 1.052599e-06 & 1.049406e-06 \\ 
\hline
3 & 2 & 1 & 3 & 4.207383e+00 & 2.698941e-06 & 6.414775e-07 \\ 
3 & 2 & 2 & 3 & 1.335376e+00 & 1.349331e-07 & 1.010450e-07 \\ 
3 & 2 & 3 & 3 & 1.058688e+00 & 6.504992e-09 & 6.144388e-09 \\ 
3 & 2 & 4 & 3 & 1.012826e+00 & 3.782273e-10 & 3.734376e-10 \\ 
3 & 2 & 5 & 3 & 1.003042e+00 & 2.753365e-11 & 2.745014e-11 \\ 
\hline
3 & 3 & 1 & 3 & 4.207383e+00 & 1.150489e-09 & 2.734453e-10 \\ 
3 & 3 & 2 & 3 & 1.335376e+00 & 6.641096e-11 & 4.973204e-11 \\ 
3 & 3 & 3 & 3 & 1.058688e+00 & 3.224905e-12 & 3.046133e-12 \\ 
3 & 3 & 4 & 3 & 1.012826e+00 & 1.004670e-13 & 9.919476e-14 \\ 
3 & 3 & 5 & 3 & 1.003042e+00 & 3.476637e-15 & 3.466092e-15 \\ 
\hline
3 & 4 & 1 & 3 & 5.166875e+00 & 1.524000e-25 & 2.949559e-26 \\ 
3 & 4 & 2 & 3 & 1.474014e+00 & 1.231139e-27 & 8.352288e-28 \\ 
3 & 4 & 3 & 3 & 1.102368e+00 & 5.433012e-27 & 4.928491e-27 \\ 
3 & 4 & 4 & 3 & 1.012826e+00 & 1.327379e-23 & 1.310570e-23 \\ 
3 & 4 & 5 & 3 & 1.003042e+00 & 6.807789e-25 & 6.787141e-25 \\
\hline
\end{tabular}
\end{center}
\label{tab::worst_all_reg_inv_conv}
\caption
    {
      We show the lowest value of
      $I$ for an entire Cartesian grid of size $32^D$.
      We vary Taylor power $P^T$, weighting
      function exponents $P^W$, and dimensionality $D$.   Keep in mind
      that the effective condition number of the problem will be $(1/\sqrt(I))$.
    }
\end{table}
\end{small}

\section{Cut Cell Geometry}
\label{sec::eb}

@@

If we use grid volumes at this point, the volume fraction
\begin{equation*}
\kappa_\ibold \equiv V_\ibold/h^D 
\end{equation*}
can be arbitrarily small ($ 0 < \kappa <= 1$).   We can also choose to
merge small volumes with larger neighbors without formal loss of
accuracy. The simple merger we use is described in
described in appendix \ref{appendix::merger}.
When merged using this algorithm, $\kappa$ can be larger than $2^D$.

Without using cell merger, the volume map in two dimensions is shown
in figure \ref{fig::unmerged2dmap}.   With cell merger, that same map
becomes the grid shown in figure{fig::unmerged2dmap}.
Tables \ref{tab::worst_unmerged_inv_conv} and
\ref{tab::worst_merged_inv_conv}
show the worst condition number for the unmerged and merged  grids
respectively while varying $P_w$ and $P_T$.   Merger does not seem to
help substantially with this issue.

@@

We show first that for a safe (low) choice of
$P_T$, even the worst condition number in a given grid can be quite
reasonable. With more aggressive choices of $P_T$, $I$ can be very
small.  The data also
show clearly that there is a connection between solvability, weighting
function, and polynomial order.  Unexpectedly, we show that for a
fixed polynomial order $P_T$, a higher weighting power $P_w$ can make the
solvability problem worse.
